\emph{mbeddr} is a projectional editor that includes a set of extensions to C'snative syntax. These extensions ease the development of embedded software basedon C and make the software engineer moreproductive~\cite{VoelterRKS13}.However, when critical systems are developed, certain guarantees of correctnessare required. For this purpose, various techniques and technologiescan be used. For example, a combination of testing, model checking, codereviews and traceability between the artifacts used throughout the developmentmight be used to build enough confidence in the final product.\vspace{2mm}\noindent\textbf{With this project we propose making use of \emph{mbeddr}'s native capabilitiesto allow the creation, maintenance and reuse of convincing technical and logicalarguments that support the claim that the C code produced using the\emph{mbeddr} front-end is certified to be correct.} \vspace{2mm}\noindentA more strategic objectiveis to (re)-establish \emph{mbeddr} as a fortiss research product, where advancedsoftware engineering tools can be prototyped. There is a natural symbioticrelationship between the \emph{fortiss-mbeddr}\markus{what is fortiss-mbeddr?}and the itemis AG \emph{mbeddr}\markus{There is only one mbeddr}:being a production tool, the itemis AG \emph{mbeddr} will be used byclients who will provide real-world problems that require advanced technicalsolutions; being a research tool, the \emph{fortiss-mbeddr} will provide atestbed to prototype such technical solutions.\markus{I am strongly againstthese two flavors! We should talk about what the two companies do with mbeddr,but not about two ``Kinds'' of mbeddr.}We place particular importance in achieving a robust and stable\emph{fortiss-mbeddr} tool such that can be used as an exploration tool both forthe industrial world and for the academic community.