Currently, one of the main bottlenecks when trying to provide an argument forthe correctness of the C code generated from \emph{mbeddr} lies in the fact thatthe code generators that transform \emph{mbeddr} C specifications into real Ccode are not verified. This amounts to saying that, although: 1) \emph{mbeddr}’sfront-end helps the developer by providing editing assistance and goodabstractions; and 2) the generated code can be verified using theCBMC\cite{KroeningT14} C model checker, there are no guarantees that thesemantics of the \emph{mbeddr} C specification is kept in the generatedcode\markus{I don't quite understand why you mention CBMC here.Doesn't it provide (some of the) assertions you are aiming for? I would omitthis here, and in a separate paragraph explain, how and why unit testing andeven CBMC are not good enough.}.This is a crucial problem for thqe adoption of \emph{mbeddr} in practice: a caseneeds to be made for the validity of the generated C code. Making this case willencourage C developers to use the tool; and its its omission may prevent \emph{mbeddr} from being used for the development of critical systems, one ofthe main domains the tool is aimed at. Verifying code generation falls in thedomain of the analysis of model transformations and can be tackled using theapproach described in\cite{Lucio2014,Oakes2015}.The language used for code generation within \emph{mbeddr} is same as the oneused within the MPS framework\markus{This statement is misleading: since mbeddris built with MPS, by definition, we use MPS' trafo languages}.Because of this, the work on verifying code generation within \emph{mbeddr} canbe naturally generalized\markus{It does not generalize. It is identical!} to theMPS framework itself, reaching in this way a broader audience for these resultsand opening perspectives for more industrial collaborations and deeperscientific insights.\levi{What is the size of the MPS community? Would this beinteresting for that community?}\markus{Yes,there are other users (Daimler,BOSCH), who could be interested in this.}\markus{Deliverable IMHO: 1 a new M2M trafo lang for MPS 2 a contract prover forthis lang 3 reimplementation of some of mbeddr's trafos with this new language,4 plus correctness proofs for these trafos. Me and the team here would help youintegrate 1 and 2 into MPS. And the help design and implement 3. You would help us do 4.}\begin{itemize}  \item Deliverables:  \begin{enumerate}    \item A prototype within \emph{mbeddr} of a model-to-model transformation languagewithin \emph{mbeddr} to replace current model-to-text code generators.	\item A prototype within \emph{mbeddr} of a pre- / post-condition contract prover formodel-to-model transformations within \emph{mbeddr}.	\item A technical proof of the correctness of the C code generator for \emph{mbeddr}.  \end{enumerate}  \item Effort: 6 man-months  \item HQP: Levi L\'ucio, Bentley Oakes  \item Collaborations: Markus Voelter will provide the requirements for both  the model transformation language to be implemented and the contract prover.  An collaboration with Markus Voelter related to this work package has been ongoinginformally during most of the year of 2015.\end{itemize}