\paragraph{\textbf{Objective}}: To establish explicit traceability mechanismsfor a C application developed in \emph{mbeddr}, from the requirements tothe generated code.\vspace{.2cm}\\Traceability is a fundamental artifact to enable certification as it allowsknowing which requirements are implemented in the final software product and howthat implementation was done. In the context of \emph{mbeddr}, traceability links allartifacts used throughout the development of embedded C software, starting froma set of requirements and finishing with the generated code. Given that a new model transformation language for code generation will beintroduced in \emph{mbeddr} by Work Package~\ref{sec:wp1}, currenttraceability mechanisms within \emph{mbeddr} will have to be reviewed andadapted. In particular, it will be necessary to build and store traces betweenthe abstract syntax element of the \emph{mbeddr} language and of the \emph{C}language.\markus{Sorry to be a PITA, but this formulation really does not make sense.There are two kinds of traceability: those traces entered manually by usersbetween model model elements (eg from code to requirements). THis is alreadydone by mbeddr, and there really is nothing to do. It's done. The other one isthe automatic trace used by MPS internally to track how, duringtransformations, nodes are transformed into other nodes. This is also done, butonly for MPS' existing trafo languages. Now, you have two options for what youcan do: 1) you make sure that your new trafo language also creates theseMPS-based traces during trafo. This is important for eg debugging. 2) you maywant to create reports on that data that can be used during certification.}\begin{itemize}  \item Deliverables:  \begin{enumerate}    \item Prototype in \emph{mbeddr} for building and storing explicit traceability    from the embedded application requirements, to the corresponding \emph{mbeddr}    specification abstract syntax, to the corresponding abstract syntax tree for    the generated C code.  \end{enumerate}  \item Effort: 2 man-months  \item HQP: Levi L\'ucio, Zaur Molotnikov, Hiwis student  \item Collaborations: Members of the IETS3 project.\end{itemize}