\paragraph{\textbf{Objective}}: To integrate the technical means provided by
Work Packages 1, 2 and 3 such that arguments for the certification of the C code
produced by \emph{mbeddr} can be built and reused in a modular
fashion.\vspace{.2cm}\\
The technical mechanisms mentioned above are pieces in the formulation of a
complete argument for the correctness of C applications created using the
\emph{mbeddr} IDE.
A complete such argument requires assembling all those pieces in a technically
and logically meaningful fashion. The result of this work implies putting
together formal and non-formal arguments that will constitute a sufficiently
strong argument such that the generated C code can be considered certified.
Coming up with a strategy for assembling those arguments will require
interaction with ongoing projects at fortiss.

% Another point of interest of
% this project is to investigate how multiple C profiles can co-exist within
% \emph{mbeddr}, together with their certification artifacts. This can
% be achieved by making use of \emph{mbeddr}'s native support for variability and
% potentially extending it. \emph{mbeddr} allows enabling or disabling certain
% groups of statements for a given program, based on a set of C's features that
% are enabled or disabled for that particular program.
% This variability will then need to be extended to the technical mechanisms
% proposed in Work Packages 1 through 3 such that each C profile can be directly
% associated to a set of activities that need to be carried out in order to
% certify C code built using that profile.

\begin{itemize}
  \item Deliverables:
  \begin{itemize}
    \item{\textbf{D4.1}:} A prototype for a method to integrate the artifacts
    built by work packages 1, 2 and 3 (code generation contracts, traceability, C profiles)
    into a unified argument for the certification of the generated C code.
% \item{\textbf{D4.2}:} A prototype for a method to introduce variability in a
% certification argument for \emph{mbeddr}. This will be achieved by introducing variability at
% the level of the technical artifacts used to build the certification argument:
% the C profiles themselves, code generation contracts, traceability reports or
% others that may arise during the execution of the project. The example profile implemented in
% Work Package 3 together with the standard \emph{mbeddr} C will be used as
% concrete example profiles to develop the method.
  \end{itemize}
  \item Effort: 9 man-months
  \item HQP: Levi L\'ucio, staff researcher, M.Sc. student, HiWi student 
  \item Collaborations: Sebastian Voss and the members of the IETS3 project on
  analysis of requirements will provide their expertise on the formulation of
  arguments of correctness for software.
\end{itemize}