Dissemination will be done primarily at the industrial level by targeting users
of the version of mbeddr built by our partners at itemis AG. Given the mechanisms we propose in the project can be used at the level of the MPS IDE, the
MPS community will also be targeted for dissemination. Foreseen dissem- ination
actions include writing user guides, online tutorials and building short videos
that can eventually integrate both the mbeddr and MPS websites. Other actions
include organising workshops together with members of the mbeddr or MPS
communities as well as hands-on tutorials. Dissemination and community building
within fortiss itself will done also using hands-on tutorials where users will
be taught about how to build certifiable C code\levi{􏰀this is maybe weak and
vague\ldots talk about dissemination with companies? Which ones?}􏰁 Additional
dissemination actions will be done by attending specialized conferences and
proposing or joining workshops in the domain in order to build academic interest
in the fortiss-mbeddr tool as a complete means for building certified C code.
We place particular importance in achieving a robust and stable fortiss- mbeddr
tool such that can be used as an exploration tool both in the industrial world
and in the academic community.

\begin{itemize}
  \item Deliverables:
  \begin{enumerate}
    \item User guide, online tutorial, video(s)
	\item Hands-on tutorial
	\item Academic papers accepted at relevant workshops, conferences and jour-
nals
  \end{enumerate}
  \item Effort: 2 man-months
  \item HQP: Levi L\'ucio
  \item Collaborations:
\end{itemize}